%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Full-Stack Developer} % Job title
    {\href{https://vocode.dev}{Vocode (YC W23)}} % Organization
    {Remote} % Location
    {Jan. 2024 - Jun. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a user-facing dashboard with Next.js and Apollo, enabling non-technical users to seamlessly interact with our core product.}
        \item {Implemented a GraphQL API layer with Strawberry and Pydantic to streamline and enhance developer productivity.}
        \item {Transitioned our core API from Supabase to plain PostgreSQL, ensuring easier deployment and scalability for our infrastructure.}
        \item {Developed the company's website using Next.js, ensuring a fast, responsive, and dynamic user experience tailored to our brand.}
      \end{cvitems}
    }

  \cventry
    {Full-Stack Developer} % Job title
    {\href{https://unicef.org}{Unicef}} % Organization
    {Remote} % Location
    {Dec. 2022 - Jan. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a responsive Figma-like web app with React, improving UI/UX and digitizing internal processes.}
        \item {Designed scalable microservices for a web app, ensuring flexibility and resilience.}
        \item {Built RESTful APIs in Node.js and Express.js for microservice communication.}
        \item {Implemented async messaging (e.g., Kafka, RabbitMQ) for responsive, decoupled microservice communication.}
        \item {Integrated JWT-based authentication and authorization (RBAC) mechanisms to secure user interactions across microservices.}
        \item {Leveraged Docker for efficient containerization and deployment.}
        \item {Used CI/CD pipelines (e.g., Jenkins, GitLab CI) for automated testing, building, and deploying microservices, ensuring continuous integration.}
        \item {Conducted load testing and tuned performance to optimize responsiveness and scalability under diverse workloads.}
      \end{cvitems}
    }

  \cventry
    {Full-Stack Developer} % Job title
    {\href{https://blum.com}{Blum}} % Organization
    {Remote} % Location
    {Nov. 2021 - Dec. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enhanced system stability by optimizing Linux kernel modules, reducing system crashes by 30\%.}
        \item {Streamlined adapter development for new catalog items, cutting integration time by 60\%.}
        \item {Improved boot speed by refining startup scripts, reducing boot time by 50\%.}
      \end{cvitems}
    }

  \cventry
    {Full-Stack Developer} % Job title
    {\href{https://www.porscheengineering.com}{Porsche}} % Organization
    {Remote} % Location
    {Dec. 2020 - Nov. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and optimized the price calculation SOAP API for Volkswagen, Porsche, and Audi car configurators.}
        \item {Integrated new products into the price calculation API, ensuring accurate and up-to-date pricing across all configurators.}
        \item {Expanded upon the existing DROOLS codebase in order to give non-technical analysts access to more functions.}
      \end{cvitems}
    }

  \cventry
    {Full-Stack Developer} % Job title
    {\href{https://cloudflight.io}{Cloudflight}} % Organization
    {Cluj-Napoca, Romania} % Location
    {Oct. 2020 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed real-time notifications with WebSockets, boosting task update visibility and enabling multiplayer capacities.}
        \item {Implemented offline functionality in the PWA, ensuring uninterrupted access.}
        \item {Integrated advanced search features, improving task retrieval speed.}
      \end{cvitems}
    }

  \cventry
    {Full-Stack Developer} % Job title
    {\href{https://vodafone.com}{Vodafone}} % Organization
    {Remote} % Location
    {Aug. 2020 - Oct. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a front-end MVP using Angular and RXJS for monitoring real-time data streams from factory sensors.}
        \item {Optimized a critical microservice by refactoring code, improving efficiency and scalability while reducing maintenance overhead.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
