%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Recommendations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Product Owner @ \href{https://urb.io}{Urbio}} % Organization/group
    {Filip Marusca} % Name
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        Vlad is more than just an experienced full-stack developer; he possesses a deep understanding of both the product and business logic, which allows him to maximize their potential. My most recent collaboration with Vlad concluded merely a month ago, and the entire process unfolded seamlessly. The completion of the project was bittersweet for me, as finding reliable and seasoned developers who go above and beyond to comprehend your product and meticulously attend to every detail is a daunting task. I wholeheartedly endorse Vlad and eagerly anticipate our future collaborations. His commitment and expertise are truly unparalleled.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CTO @ \href{https://vocode.dev}{Vocode}} % Organization/group
    {Ajay Raj} % Name
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        Vlad is an exceptional full-stack developer. What really stood out to me working with him was his ability to operate with low context and his commitment to building things in the right way - it made it painless to work with him in a timezone where we were only able to overlap for a few hours a day. I highly recommend him for future opportunities.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Developer @ \href{https://authorium.com}{Authorium}} % Affiliation/role
    {Stephen Handley} % Organization/group
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        Vlad is an ideal collaborator for product engineering teams. He is a diligent and creative engineer with 
        an innate sense for usability and product design, and his sense of humor and calm demeanor 
        make him a joy to work with.
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
